Summary of Changes

### 2021-03-12 response_letter/response-letter.tex

{\em Authors response:}
Thanks a lot for your correction. We have indicated the omission in the revision
(see Section II.B, pp.4).
%as following:
%\begin{itemize}
%\item (we omit some irrelevant content due to space limitation,
%such as the temporary variables \%1 and \%2 which are from stack allocation).
%\end{itemize}
As you pointed out, \%1 and \%2 are indeed two temporary
variables from stack allocation and we omit them.

\smallskip
\smallskip
\smallskip
\noindent {\bf 6) Proofread the paper more thoroughly, as there are
several grammatical mistakes and non-idiomatic wordings. There is
also a typo in Section III.A: ``[...] \%18 has been cas(T)ed from [...]''. }

{\em Authors response:}
Thanks for your correction and suggestion. We have corrected the typo in the
revision. And we have reviewed the revision carefully several times and fixed
some mistakes.

\smallskip
\smallskip
\smallskip
\noindent {\bf As a final note, the hypervisor-based protection
actually does more than thwarting ret2usr attacks. It also protects
against kernel code reuse, which is a common SMEP bypass.}

{\em Authors response:}
Thanks for your information. We agree with your opinion. Indeed, in the revision,
we have leveraged several SMEP/SMAP bypass attacks to clarify that our
hypervisor-based protection can also protect against kernel code-reuse
attacks (see Section IV.A, pp.11).

%Thanks for your note, we have used two examples about SMEP bypass attacks
%to clarify that our hypervisor-based protection can also protect against
%kernel code-reuse attack (see Section IV.A,pp.10).

\section{Response to Reviewer Two}

\noindent {\bf Strengths:

- Prototype implementation

- Good performance\\
Weaknesses:

- Contribution not clear

- Explanation of the idea requires revision

- Security analysis not convincing }

{\em Authors response:}
Thanks for the summary. We will respond to your concerns in the following.

\smallskip
\smallskip
\smallskip
\noindent {\bf Modern kernels are written in unsafe languages like
C/C++, and prone to memory corruption vulnerabilities. Attackers
exploit these vulnerabilities to overwrite code pointers, which
are afterwards used by the application, to hijack the control
flow, and get full control of the system. One prominent defense
against control-flow hijacking attacks is control-flow integrity
(CFI) which verifies each code pointer before it is used as a branch
target. This paper presents the design and implementation of CFI
for operating system kernels, called \TheName{}. In contrast to user
mode CFI, kernel CFI comes with additional challenges as the kernel
makes heavy use of single code pointers in various data structures.

In general, the presented design makes a solid impression.
\TheName{} is a compiler extension that instruments the kernel to enforce
CFI checks before each indirect branch. Further, \TheName{} utilizes a
trusted hypervisor to protect the context data of interrupts. This is
important because the interrupt context contains the saved instruction
pointer. The performance evaluation indicates an acceptable average
performance overhead of less than 5\%. }

{\em Authors response:}
Thanks for the summary and comments.

\smallskip
\smallskip
\smallskip
\noindent {\bf The main issue of the paper is that all the previous
described design of \TheName{} is a retrofitted version of the authors
previous work `Comprehensive and efficient protection of kernel control
data' [27]. Hence, it is a bit confusing that large parts of the paper
are dedicated to explaining and evaluating this design. }

{\em Authors response:}
Thanks for your patience. We fully understand what you're confusing
and we do borrow the instrumentation scheme \emph{indexed hooks} in our
previous work `Comprehensive and efficient protection of kernel control
data'. However, as mentioned by you in the following, the main contribution
of this paper is that it leverages a retrofitted context-sensitive and
field-sensitive pointer analysis (rather than the dynamic profiling approach
in the previous work) which greatly improves the precision of
kernel CFG. Note that to enforce fine-grained CFI for an operating system
kernel, the key is to get a precise and fine-grained CFG of it.
After obtaining the fine-grained CFG, it is an intuitive thing to
enforce fine-grained CFI since there have been some fairly mature
solutions. We leverage \emph{indexed hooks} rather than the original label-based
approach as \emph{indexed hooks} solved the destination equivalence problem, which
could possibly lead to coarse-grained CFI.

We have made a further clarification in the revision (see Section VI, pp.14).

%Thank you for your patience. We fully understand what you're confusing
%and we do borrow the instrumentation scheme (i.e., indexed hooks) in our
%previous work `Comprehensive and efficient protection of kernel control
%data'. However, just like what we said in the paper (see Section I, pp.3) and
%you mentioned in the following, the main contribution of this paper lies in
%two aspects. One is the retrofitted context-sensitive and field-sensitive pointer
%analysis which greatly improves the precision of kernel CFG. Another is
%the effective hypervisor-based protection mechanism for interrupt context
%which verifies every interrupt control data including IP and CS in kernel
%stack. Combining both of them, \TheName{} can effectively defeat those
%formidable ret2usr and kernel code-reuse attacks.

\smallskip
\smallskip
\smallskip
\noindent {\bf The actual contribution of the paper is the difference
in inferring the policy that is enforced by CFI run-time checks.
The previous work [27] used a dynamic analysis while this paper uses
a compiler-based approach. In particular, this paper bases their policy
on function signatures (return type, number and type of arguments).
Unfortunately, this is a known technique and published [a] (slide 23)
which weakens the scientific contribution. However, this could be
compensated by providing a very strong evaluation and documentation.

[a] https://pax.grsecurity.net/docs/PaXTeam-H2HC15-RAP-RIP-ROP.pdf }

{\em Authors response:}
Thank you. We agree that the function signature-based policy is not
a novel idea, though it is not an easy task to implement
such a policy in a large code base.
Further, we want to clarify that our pointer analysis
approach is not merely based on function signatures. Indeed, to improve
the precision of the function pointer's point-to set, we introduce a new
vector, i.e., \emph{struct location vector}, to infer the targets for
indirect function invocations. We introduce such a vector as we observe
that there are a large number of function pointer initializations and assignments inside
struct variables in kernel space, and the function pointer
locates in the same field of the struct in its lifetime, i.e.,
from the initialization or assignment to be consumed by indirect function calls.
Combining \emph{struct location vector} with function signature-based policy,
it largely reduces the number of targets of indirect call/jmp instructions
(average $13.14$ for each indirect call/jmp instruction) (see Section II.B, pp.4).
Additionally, as you suggested in the following, we have
performed a further security evaluation using a ROPgadget tool to find and analyze
the remaining gadgets after our instrumentation, and the results show that none of these gadgets could
be used to launch an effective ROP attack (see Section IV.A, pp.11).
%our approach is able to prevent
%all ROP attacks (see Sectiion IV.A, pp.10).

%Thanks for your suggestion. In fact, our pointer analysis approach
%is not entirely based on function signatures which are just applied
%in very few cases (e.g., a function pointer is not from any field of
%any structure). Actually, our approach bases the struct location vector
%of a function pointer which is more precise than the simple function
%signatures, and largely reduces the number of targets of indirect call/jmp
%instructions (average 13.14 for each indirect call/jmp instruction).
%At the same time, we provided a more strong security evaluation using
%ROPgadget to find the remaining gadgets as you suggested, and the result
%shows that our pointer analysis is precise enough to prevent against all
%ROP attacks (see Section IV.A,pp10).

\smallskip
\smallskip
\smallskip
\noindent {\bf This leads to the second shortcoming of the paper.
The paper would greatly benefit from revising Section II.B. While
such a detailed explanation of the used techniques is desirable
for the implementation section, the authors should also include a
more high-level description of their technique that does not require
compiler background knowledge.}

{\em Authors response:}
Thank you very much and it is a good point. In the revision, we have followed
your suggestion and revised Section II.B carefully.

\emph{First}, we have provided a formal definition of \emph{struct location vector}.
In particular, we define the \emph{struct location vector} of a function pointer
as the location of the function pointer member in a (nested) struct.
To better represent the cases in nested structs, we use the name of the
struct, the element's order number, and the nested member's order numbers
to reach the function pointer member in the struct to denote its
\emph{struct location vector}. Thus, the \emph{struct location vector} of a
function pointer is denoted as
\emph{(\%struct.name, ele\_order, mem\_order\_$1$, ... , mem\_order\_$i$, ...)}
(\emph{ele\_order} denotes the element' order number in a \emph{\%strut.name}\_typed
array, and \emph{mem\_order\_$i$} denotes the member's order number of layer
\emph{$i$} in \emph{\%struct.name} struct to reach the function pointer; $i$$>=1$)
(see Section II.B, pp.4).

\emph{Second}, we have introduced a more high-level description of our pointer
analysis with a basic worklist algorithm that does not require compiler
background knowledge to understand (see Algorithm 1, pp.4).
After that, to describe our algorithm more intuitively, we leverage a simple
example program to present the process to determine the point-to sets of
indirect function calls (see Figure 1 and 2, pp.5).

\emph{Third}, we have further made our main conceptual ideas and innovations
clearer in the revision (see Section II.B, pp.4).

\smallskip
\smallskip
\smallskip
\noindent {\bf For a strong evaluation, there are couple of issues
which need to be addressed: }

\noindent {\bf 1) It was shown and the community agreed
that the AIR metric is not very useful [57]. Hence, the paper would
greatly benefit from an (semi-)automatic analysis of the remaining
attack surface which means looking at the remaining gadgets and if
they could be used in an attack. }

{\em Authors response:}
Thank you very much for the constructive comment.
Following your suggestion, we have figured out the remaining gadgets
in the original and instrumented Linux kernel using the open-source tool
ROPgadget. As a result, ROPgadget found $44,063$ gadgets in the original
Linux kernel and $841$ gadgets in the instrumented Linux kernel. We
checked all these $841$ gadgets and confirmed that none of them can be
reached through a control flow which is allowed by our fine-grained CFG.
Therefore, none of these gadgets could be leveraged to launch an effective ROP
attack (see Section IV.A, pp.11).

\smallskip
\smallskip
\smallskip
\noindent {\bf 2) The choice of benchmarking test is not always
clear: CPU heavy user mode benchmark (SPEC CPU) are expected to not
have any serious performance degradation when kernel CFI is applied.
Further, it is not clear how single arithmetic operations are meaningful
in this context. Could \TheName{} be applied to the SPECCPU benchmarks?}

{\em Authors response:}
Thanks for your comments. We also notice that it seems to be no
serious performance overhead on SPEC CPU benchmark when kernel CFI is
applied. To further measure the performance overhead imposed by our approach,
we have followed your suggestion and applied \TheName{} to four benchmarks
in SPEC CPU2006 benchmark suite, i.e., 401.bzip2, 403.gcc, 429.mcf, and 458.sjeng.
These benchmarks depend on the \emph{libc} library as well as some objects
in C runtime library (e.g., crt1.o, crti.o, crtn.o). To achieve that,
we need to instrument the benchmark programs as well as the dependencies.
%And each one depends on the \emph{libc} library and some
%default libraries in GCC (e.g., \emph{libgcc\_eh}) as well as some objects
%in C RunTime Library (e.g., crt1.o, crti.o, crtn.o). To achieve that, for each benchmark,
%we instrumented the program and all above dependent libraries/objects, and linked them together statically.
The evaluation results show that the performance overheads introduced by
401.bzip12, 403.gcc, 429.mcf, and 458.sjeng are $7.18$\%, $4.13$\%, $12.03$\%, and
$10.12$\%, respectively. The details can be found in Table V, pp.12.

On the other hand, it seems to be no any performance overhead on the arithmetic
operations in LMbench. The possible reason is that these operations might not
go through enough instrumented sites in the kernel. We have removed the
single arithmetic operations in LMbench evaluation in the revision (see Figure 8, pp.12).

\smallskip
\smallskip
\smallskip
\noindent {\bf How about testing the impact on real-world applications
with the help of the Phoronix benchmarking suite? }

{\em Authors response:}
Thanks for your suggestion. In the revision, we have selected five
representative real-world applications in the Phoronix Test Suite,
i.e., compress-7zip, postmark, nginx, cachebench, and network-loopback,
which stand for the performance behaviors in processor, disk, system, memory, and
network, respectively, to evaluate the performance overhead incurred by our
approach. The results show that the overhead is acceptable ($5.39$\% for \emph{New-f} and
$9.89$\% for \emph{New-f+i} on average, respectively). The details
can be found in Table II, pp.12.

\smallskip
\smallskip
\smallskip
\noindent {\bf Is it possible break the results further down to see
the impact on the forward/backward edge protection? }

{\em Authors response:}
This is a good point. As mentioned earlier, we have applied our CFI enforcement
to four benchmarks (i.e., 401.bzip2, 403.gcc, 429.mcf, and 458.sjeng) in the
SPEC CPU2006 benchmark suite. At the same time, we also achieve the goal to
break the results down by only instrumenting indirect call/jmp (\emph{New-icall}) or
call/ret (\emph{New-ret}) instructions, to see the impact on the forward/backward
edge protection. The results show that \emph{New-ret} incurs most of the
overhead ($7.33$\% on average) while \emph{New-icall} incurs very little ($0.96$\% on average),
and the sum overhead ($8.29$\%) incurred by (\emph{New-icall}) and (\emph{New-ret}) is
roughly equal to the overhead incurred by \emph{New-f} ($8.37$\%), which is reasonable.
We believe that the overheads introduced by \emph{New-icall} and \emph{New-ret} depend on the
executed times of our instrumented indirect call/jmp and ret instructions.
The results can be found in Table V, pp.12.

%Supposing each
%call instruction is executed once, we can also roughly guess the ratio of incurred overhead between the
%\emph{New-icall} and \emph{New-ret} by the number of indirect call/jmp and
%all call instructions (not ret instructions, as a ret instruction in a function
%\emph{f} could be executed several times by calling the function \emph{f} several
%times at different call cites). For example, in 401.bzip2, there are $302$ indirect call/jmp and
%$4,408$ call instructions, and the actual ratio ($7.46$\%) of overhead between the \emph{New-icall} ($0.51$\%)
%and \emph{New-ret} ($6.84$\%) is roughly equal to $302$/$4,408$ ($6.85$\%).
%The details can be found in Section IV.B, pp12.

%Thank you for such a good suggestion. As mentioned above, we have applied
%our CFI enforcement to several programs (e.g., 401.bzip2) in the SPECCPU
%benchmarks. At the same time, we also achieve the goal to break the results
%down by only with indirect call/jmp or ret instructions to be instrumented, to
%see the impact on the forward/backward edge protection. In order to have an
%intuitive feeling for performance results, We also count the number of
%indirect call and ret instructions respectively. All details can be found
%in Section IV.B,pp11.

\smallskip
\smallskip
\smallskip
\noindent {\bf It would be nice to see a discussion on the impact of
the call/ret stack.}

{\em Authors response:}
Thanks for your suggestion. In the revision, we have raised the discussion
in Section V, pp.13. Specifically, the original call instruction pushes a
return address on the stack and then jumps to the destination, while our scheme
pushes a table index instead and then jumps. On the other hand, in original convention
every function pointer stores a function address, while our scheme replaces the address
with a table index. This instrumentation has changed the semantic of the data.
In some special cases, it might lead to a fault. For example, when a function
pointer is compared with another value by a CMP instruction, instead of only
being consumed by an indirect call/jmp instruction. Although so far we have not
encountered such cases in our prototype, we can recover the original control data
with its index before such usage.

\smallskip
\smallskip
\smallskip
\noindent {\bf Nit Picks:

P2: verifies those information $->$ that

P5: So we put $->$ So, we put

P12: thus it introduces $->$ thus, it introduces }

{\em Authors response:}
Thank you very much for your correction. We have fixed the mistakes in the revision.

\section{Response to Reviewer Three}

\noindent {\bf This paper presents fine-grained control-flow integrity
(\TheName{}) for operating system kernel code. \TheName{} is based on a
static analysis and instrumentation LLVM pass to identify the set of
allowed branch targets for each indirect branch and so-called indexed
hooks to enforce CFI checks at run-time. In addition, it maintains an
interrupt stack to detect attacks that overwrite return addresses
during a context switch. }

{\em Authors response:}
Thank you for the summary.

\smallskip
\smallskip
\smallskip
\noindent {\bf  Memory corruption attacks hijack the program's control
flow to induce malicious program actions. Control-flow integrity (CFI)
mitigates these attacks by enforcing that the program's control flow
follows a legitimate path in the program's pre-defined control-flow graph.
However, existing schemes are either coarse-grained or do not target
kernel code. This paper aims to tackle these limitations by developing
\TheName{}. Given that most work in this area target user-land code, I
appreciate that this paper targets instead the kernel code. However, the
paper does not describe the challenges when applying CFI to kernel code.
One gets the impression that this is mostly an engineering task rather
than developing any new mechanisms. As such, I fear that the paper's main
contribution is rather limited and incremental. }

{\em Authors response:}
Thank you very much for the constructive comments. In the revision, we
have followed your suggestion and presented three additional challenges when
applying CFI in kernels (the details can be found in Section I, pp.2).

The first challenge is due to the asynchronous nature of context switching
and interrupt handling in kernel space. In particular, when an interrupt
occurs, the interrupted program's context information is saved to memory
for later restoring when the program is resumed. Note that the saved
context information could be possibly tampered with by attackers to hijack
the control flow. Different from the control-flow transfer with an
indirect call/jmp or ret instruction, we cannot predetermine when and where
an interrupt may occur, as interrupts could occur at any time or any valid
instruction boundary.

The second challenge comes from the heavy use of single code pointers in
various structures in kernel code, and these pointers may scatter across
the whole kernel. To enforce fine-grained CFI for the
kernel, it requires to identify all these code pointers and leverage them to
infer the point-to set for each indirect function call, which is not an
easy task to implement.

The third challenge is that the performance overhead introduced by the
enforcement should be as low as possible, as the operating system kernel is
the foundation for all the applications.

%It is our negligence for not pointing
%out the challenges when applying CFI to kernel code. The first challenge is to
%complete a sufficiently precise point-to analysis for indirect call/jmp instructions,
%as the kernel makes heavy use of single code pointers in various data structures.
%The second challenge is to achieve the protection for interrupt context in kernel,
%as we cannot predetermine when and where an interrupt may occur. Interrupts
%could occur at any time or any valid instruction boundary in both user and kernel
%space. We have revised it in Section I,pp3 in the revision.

\smallskip
\smallskip
\smallskip
\noindent {\bf In general, the paper is well-written and attempts to
describe the low-level implementation details based on example code.
On the other hand, the main conceptual ideas and innovations are not
really described. }

{\em Authors response:}
Thanks for the comments and criticism. We have revised Section II.B carefully
and made our main conceptual ideas and innovations clearer in the revision.

### 2021-03-12 response_letter/response-letter.tex

\emph{First}, we have provided a formal definition of \emph{struct location vector}.
In particular, we define the \emph{struct location vector} of a function pointer
as the location of the function pointer member in a (nested) struct (see Section II.B, pp.4).

\emph{Second}, we have introduced a more high-level description of our pointer
analysis with a basic worklist algorithm that does not require compiler
background knowledge to understand (see Algorithm 1, pp.4).
After that, to describe our algorithm more intuitively, we leverage a simple
example program to present the process to determine the point-to sets of
indirect function calls (see Figure 1 and 2, pp.5).

\emph{Third}, we have described our main innovation clearly in the revision.
Specifically, the main innovation of our retrofitted point-to analysis is that
we introduce a new vector, called \emph{struct location vector}, to infer the
targets for indirect function calls. This is reasonable as we observe that
there are a large number of function pointer initializations and assignments inside
struct variables in kernel space, and the function pointer locates in the
same field of the struct in its lifetime, i.e., from the initialization or assignment to
be consumed by indirect function calls. Combining \emph{struct location vector}
with function signature-based policy, it largely reduces the number of targets
of indirect call/jmp instructions (average 13.14 for each indirect call/jmp
instruction) (see Section II.B, pp.4).

\smallskip
\smallskip
\smallskip
\noindent {\bf The presented approach for points-to analysis seems
reasonable to me and the evaluation demonstrates a significant
reduction of the target branch set. Unfortunately, the paper does not
really compare the target branch set to previous work in this area. }

{\em Authors response:}
Thanks a lot. In the revision, we have provided the comparison of the
reduction of the target branch set to three previous work in this area.
The results show the AIR metric of \TheName{} (99.998\%) is better than
bin-CFI (98.86\%), KCoFI (98.18\%) and Ge's work [1] (99.6\% for return targets and
99.1\% for indirect call/jmp targets).
%Imagine an x86 program with $1$MB code, \TheName{}
%only allows $20$ targets, while bin-CFI, KCoFI and Ge's work still allow $11,400$,
%$18,200$ and $4,000$/$9,000$ targets, respectively. However, recent attacks
%on coarse-grained CFI enforcement show
%that an adversary usually requires only a small part of unintended control flows
%to realize her purpose.
The details can be found in Section IV.A, pp.10.

[1] X. Ge, N. Talele, M. Payer, and T. Jaeger, ``Fine-grained control-flow
integrity for kernel software,'' in Security and Privacy (EuroS\&P), 2016 IEEE
European Symposium on, pp.179-194, IEEE, 2016.

\smallskip
\smallskip
\smallskip
\noindent {\bf The modified interrupt handling to protect return
addresses used in context switches leverages a shadow stack like
approach. I am unsure about the novelty of this approach.
Further, I miss a justification that leveraging a hypervisor to
protect the interrupt handling resembles a reasonable approach. }

{\em Authors response:}
Yes, we do leverage a shadow stack like approach (called interrupt
stack) to protect control data in the interrupt context.
As a usual approach, a number of systems use it to provide protection
for return addresses pushed on the stack by function calls.
However, the difference between shadow stack approach and our protection
mechanism is that interrupts could occur at any time or any valid
instruction boundary, but function calls occur at the fixed
instruction boundaries. In other words, it can be predetermined
when and where an return address will be pushed on the stack
(i.e., when a call instruction is being executed), so that the shadow
stack approach can protect it by instrumenting all the call (and ret)
instructions. However, kernel itself cannot predetermine when and where
an interrupt may occur and it is impossible for us to do that by
instrumenting every instruction in the kernel. As a result, we propose
the hypervisor-based approach to protect control data in the interrupt
context, as the hypervisor can take over the guest VM when an interrupt
happens. So that we can backup the control data in the hypervisor for
later verification when returning from the interrupt handler.

Further, we want to clarify that the main novelty of this paper
is that it leverages a retrofitted context-sensitive and field-sensitive
pointer analysis to obtain the fine-grained CFG of the kernel, which
greatly improves the precision of the result. In particular, we
introduce a new vector, i.e., struct location vector, to infer the targets
for each indirect invocation. It largely reduces the number of targets of
indirect call/jmp instructions (average 13.14 for each indirect call/jmp
instruction).

%Thank you for the comments. Yes, we do leverage a shadow stack like
%approach (called interrupt stack) to protect the interrupt control
%data. However, the biggest difference between shadow stack and our
%protection mechanism is that interrupts could occur at any time or
%any valid instruction boundary, but function calls occur at the fix
%instruction boundaries. In other word, it can be predetermined when
%and where the kernel will push return address to stack (when and
%where a call instruction is about to be executed.) so that shadow
%stack can protect it by instrumenting all call instructions; However,
%kernel ifself cannot predetermine when and where an interrupt will
%happen and it is also impossible to instrument every instructions in
%kernel, thus we propose the hypervisor-based approach to protect
%interrupt context as hypervisor can take over the guest VM when an
%interrupt happens so that we can backup the interrupt context in
%hypervisor for verification when returning from interrupt handler.

\smallskip
\smallskip
\smallskip
\noindent {\bf The evaluation is based on several well-known
benchmark programs and demonstrates the overhead is acceptable.
The security evaluation also includes tests against existing exploit
payloads. \TheName{} is able to prevent the exploits of the RIPE testbed. }

{\em Authors response:}
Thanks for the summary. We have added several new security and performance
evaluation results in the revision (see Section IV, pp.10-13).

\smallskip
\smallskip
\smallskip
\noindent {\bf I miss any comparison to a recent, very closely related
work on kernel-CFI: ``Fine-Grained Control-Flow Integrity for Kernel
Software'' (EURO SP 2016). }

{\em Authors response:}
Thank you very much for the information. We have done a comparison to that
recent work (i.e., ``Fine-Grained Control-Flow Integrity for Kernel
Software'') in the revision (see Section VI, pp.14). In contrast, the biggest
advantage of \TheName{} is that our pointer analysis is based on LLVM IR code
while that work is based on source code. As the IR code of compiler is a
low-level strongly-typed language-independent representation which preserves
most of the type information and enough context information that are required
by our analysis, it is an effective way to determine the target set
of an indirect function call by traversing the function pointer's
transfer process in IR code. As a result, we achieve a higher precision.
For instance, the AIR metric of \TheName{} is 99.998\%, which is better than
that work (99.6\% for return targets and 99.1\% for indirect call/jmp
targets).
%Additionally, we provide a comprehensive protection for control data
%in the interrupt context, while that work does nothing in this aspect which
%obviously exposes to adversary as an available attack surface. Finally, we
We also compare the performance to that work in our revision (see
Section IV.B, pp.12). The results show that the performance overhead
incurred by \TheName{} is smaller than that work.

\end{document}
